---
title: "Senegal HIV model"
author: "Fabricia F. Nascimento"
date: "`r Sys.Date()`"
output:
  rmarkdown::pdf_document:
    fig_caption: true
    df_print: kable
    highlight: pygments
    citation_package: biblatex
bibliography: bib/senegalHIVmodel.bib
fontsize: 12pt
vignette: >
  %\VignetteIndexEntry{Senegal HIV model}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.table.format = "latex")
```

# Introduction

* Phylogenetic trees were estimated for each HIV-1 subtype: B, C, and 02_AG;
* Using information on when sequences were collected, a phylogenetic tree
in which branch length were in units of calendar times were also estimated;
* These 3 dated phylogenetic tree were merged into a single tree;
* Each tip of the pylogenetic tree was associated to a state (see section below);
* If a tip could not be associated to a state (because of missing information in the metadata),
this particular tip was removed from the dated tree;
* The dated phylogenetic tree in which all tips could be assigned to a state 
were then used with phydynR to estimate the transmission rates and parameters of the model
(see below for more information on which parameters we are estimating).


# The Model
The model we fit is based on the structured coalescent models [@Volz2012]. These models are used to estimate epidemiological parameters using a phylogenetic tree and information on states of each tip of the tree. These states are discrete-trait information representing each sequence.

In our mathematical model we have 4 different discrete-traits associated to each DNA sequence:

* $gpf$ = infected heterosexual females from the general population;
* $gpm$ = infected heterosexual males from the general population;
* $msm$ = infected male that have sex with other men;
* $src$ = source sample, which are infected individuals that are from other countries and not from Senegal. 

## Stage of infection

We fit the HIV epidemic in Senegal using ordinary differential equations (ODE) and only 1 stage of infection. This means that infected individuals would die and not recover from the infection. In our model we represented it as $\gamma$ rate. We used 1 stage of infection, because the metadata available for the Senegal sequences did not have information that we could use to determine the stage of HIV infection at the time the samples were collected. 

## How transmissions were modelled?

* An infected $msm$ ($I_{msm}$) could transmite to another $msm$ with probability $p_{msm2msm}$
* An infected $msm$ ($I_{msm}$) could transmit to a $gpf$ with probability  $(1 - p_{msm2msm})$
* An infected $gpf$ ($I_{gpf}$) could transmit to a $gpm$ with probability $p_{gpf2gpm}$
* An infected $gpf$ ($I_{gpf}$) could transmit to a $msm$ with probability $(1 - p_{gpf2gpm})$
* An infected $gpm$ ($I_{gpm}$) could also transmit to a $gpf$. For this event, we used the risk ratio of a male to transmite to a female, and fixed it to $1.02$. This is the parameter $male_{x}$ of our model.

## How about HIV incidence rate?

We also modelled the HIV incidence rate as a funtion of time ($t$) in $msm$ and the $gp$ (general population) as different spline functions [@Eilers1996], that in our ODEs are represented by $\lambda(t)$ and $\mu(t)$, respectively.

## The $source$ compartment

Finally, to model the HIV epidemic in Senegal, we also added an additional compartment named "source" ($src$), that represents the rate in which HIV lineages are imported to Senegal from other countries. We modelled this as a constant efective population size rate with two parameters to be estimeted -- $srcNe$: the effective source population size; and the $import$ rate. Because the number of imported HIV balances the number of exported HIV, the infected $src$ individuals along time are not represented in the ODEs. 

## The ODEs or mathematical model equations


$\dot{I}_{gpf} = male_x \mu(t) I_{gpm} + (1 - p_{msm2msm}) \lambda(t) I_{msm} - \gamma I_{gpf}$

$\dot{I}_{gpm} = p_{gpf2gpm} \mu(t) I_{gpf} - \gamma I_{gpm}$

$\dot{I}_{msm} = (1 - p_{gpf2gpm}) \mu(t) I_{gpf} + p_{msm2msm} \lambda(t) I_{msm} - \gamma I_{msm}$


# Estimation of epidemiological parameters

For the Senegal HIV model, we are estimating the parameters using a Markov chain Monte Carlo (MCMC) as implemented in the R package [BayesianTools]("https://github.com/florianhartig/BayesianTools").

## Parameters to be estimated and priors

**Parameters for estimating the spline function for the _gp_:**

* _gpsp0_: prior chosen with mean around 1.1
* _gpsp1_: prior chosen with mean around 1.1
* _gpsp2_: prior chosen with mean around 1.1
* _gpsploc_

**Parameters for estimating the spline function for the _msm_:**

* _msmsp0_: prior chosen with mean around $R_0 = 1.1$
* _msmsp1_: prior chosen with mean around $R_0 = 1.1$
* _msmsp2_: prior chosen with mean around $R_0 = 1.1$
* _msmsploc_

**Parameters that controls the _src_:**

* _import_: prior chosen with mean around $0.03$
* _srcNe_: prior chosen with mean around $0.05$

**Probability of certain events to occour:** 

* _pmsm2msm_ : prior chosen with mean around $0.80$
* _pgpf2gpm_ : prior chosen with mean around $0.80$

**Initial population sizes:**

* _initgp_: prior chosen with mean around $10$
* _initmsm_: prior chosen with mean around $10$

See Table 1 for a list of parameters that we are estimating and the priors used. 
Note that lower and upper bounds for the priors were used to keep the posterior 
distribution at sensible values when using the BayesianTools R package. If such 
bounds were not provided negative or very high values, when low values were expected,
could be proposed during the MCMC. 

```{r echo = FALSE}
Parameter = c("Spline shape gp0",
              "Spline shape gp1",
              "Spline shape gp2",
              "Spline interval gp",
              "Spline shape msm0",
              "Spline shape msm1",
              "Spline shape msm2",
              "Spline interval msm",
              "Infectiouness ratio from male to female",
              "Importation rate",
              "Effective population size of src",
              "Probability of infected msm to infect another msm",
              "Probability of infected gpf to infect a gpm",
              "Initial number of infected msm",
              "Initial number of infected gp") 
`Symbol in R` = c("gpsp0",
                  "gpsp1",
                  "gpsp2",
                  "gpsploc",
                  "msmsp0",
                  "msmsp1",
                  "msmsp2",
                  "msmsploc",
                  "maleX",
                  "import",
                  "srcNe",
                  "pmsm2msm",
                  "pgpf2gpm",
                  "initmsm",
                  "initgp") 
Priors = c("Gamma(3, 3/1.1)",
             "Gamma(3, 3/1.1)",
             "Gamma(3, 3/1.1)",
             "U(1978, 2014)",
             "Gamma(3, 3/1.1)",
             "Gamma(3, 3/1.1)",
             "Gamma(3, 3/1.1)",
             "U(1978, 2014)",
             "Fixed(1.02)",
             "Exp(30)",
             "Exp(20)",
             "Beta(16, 4)",
             "Beta(16, 4)",
             "Exp(1/10)",
             "Exp(1/10)")
Lower = c("0.01",
             "0.01",
             "0.01",
             "1978",
             "0.01",
             "0.01",
             "0.01",
             "1978",
             "Not applicable",
             "0",
             "0.0001",
             "0.1",
             "0.1",
             "1",
             "1")
Upper = c("5",
             "5",
             "5",
             "2014",
             "5",
             "5",
             "5",
             "2014",
             "Not applicable",
             "0.30",
             "0.30",
             "1",
             "1",
             "300",
             "300")
data_list = data.frame(Parameter, `Symbol in R`, Priors, Lower, Upper) 
data_list <- as.matrix(data_list)
colnames(data_list)<-c("Parameter","Symbol in R",
                       "Prior", "Lower", "Upper")

kable_table <- knitr::kable(data_list, booktabs = T, caption =  "Parameter definition, symbols used in the ODEs, priors with lower and upper bounds")
kableExtra::kable_styling(kable_input = kable_table,
                          latex_options = c("striped", "scale_down"),
                          full_width = FALSE, position = "center")

```

# Status of analysis

## Part 1
I have started estimating the parameters of the model using phydynR.
The first round of analysis, I did not estimate the initial population size of 
_gp_ and _msm_, and I fixed maleX to 2.0. After meeting with Erik, he explained
that these results are strange given that the estimated values for the spline function
(the 3 shape parameters) should follow a trend of decreasing rather than increasing. 
For example: $gpsp0 > gpsp1 > gpsp2$

See attached pdf file (results_part1.pdf). In this pdf, the density plots represent 
several runs that were merged to achieve ESS for each parameter above 1,000.
The black line represents 11 merged independent MCMC that each were run for 18,000 
iterations, while the blue line represents 10 merged independent MCMC that each 
were run for 21,000 iterations. The upper and lower bounds for the priors used 
to generate these runs were sligtly different for the one in Table 1. 

## Part 2
I am currently estimating the parameter values by additionally estimating the
initial population sizes for _gp_ and _msm_, and fixing maleX to 1.02.

I still don't have the results for these new analysis, and I am expecting to have 
them by next week.


# References
