---
title: "Senegal HIV model"
author: "Fabricia F. Nascimento"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Senegal HIV model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette will demonstrate how to estimate HIV transmission rates using DNA sequences from Senegal. This also provides a guidance on how analysis described in Nascimento, (...), Volz, 2018 was carried out. 

## Basic requirements
This vignette assumes that you know the basics of R and have the following packages already installed:

* devtools: useful for installing packages directly from github         repository, for example. 
* phydynR: it implements the coalescent simulation and likelihood       function for phylodynamics analysis
* akima: this package is necessary for interpolation of data (used      for the calculation of the likelihood by the phydynR package)
* BayesianTools: package for Bayesian inference

### Load the necessary packages:
```r
  library(phydynR)
  library(akima)
  library(BayesianTools)
```

## The Model
The model we fit is based on the structured coalescent models (REF HERE). These models are used to estimate epidemiological parameters using a phylogenetic tree and information on states of each tip of the tree. Theses states are discrete-trait information representing each sequences.

In our mathematical model we have 4 different discrete-traits, that we further explain in along this vignette:

* $gpf$ = HIV sample from the general population -- females;
* $gpm$ = HIV sample from the general population -- males;
* $msm$ = HIV sample from men that have sex with other men;
* $src$ = source sample, which are HIV samples from individuals that are from other countries and not from Senegal 

### Stage of infection

We fit the HIV epidemic in Senegal using ordinary differential equations (ODE) and only 1 stage of infection. This means that infected individuals would die and not recover from the infection. In our model we represented it as $\gamma$ rate. We used 1 stage of infection, because the metadata available for the Senegal sequences did not have information that we could use to determine the stage of HIV infection at the time the samples were collected. 

### How transmissions were modelled?

* An infected $msm$ ($I_{msm}$) could transmite to another $msm$ with probability $p_{msm2msm}$
* An infected $msm$ ($I_{msm}$) could transmit to a $gpf$ with probability  $(1 - p_{msm2msm})$
* An infected $gpf$ ($I_{gpf}$) could transmit to a $gpm$ with probability $p_{gpf2gpm}$
* An infected $gpf$ ($I_{gpf}$) could transmit to a $msm$ with probability $(1 - p_{gpf2gpm})$
* An infected $gpm$ could also transmit to a $gpf$. For this event, we used the risk ratio of a male to transmite to a female, and fixed it to $2.0$. This is the parameter $maleX$ of our model.

### How about HIV incidence rate?

We also modelled the HIV incidence rate as a funtion of time ($t$) in $msm$ and the $gp$ (general population) as different spline functions (REF HERE), that in our ODEs will be represented by $\lambda(t)$ and $\mu(t)$, respectively.

### The $source$ compartment!

Finally, to model the HIV epidemic in Senegal, we also added an additional compartment named "source" ($src$), that is reprsent the rate lineages are imported to Senegal from other countries. We modelled this as a constant efective population size rate, with two parameters to be estimeted in our models -- srcNe: the effective source population size; and the $import$ rate. Because, as mentioned, these are modeled as constant effective population size, the infected $src$ individuals along time are not represented in the ODEs below. 


The ODEs, or model equations, are:

\begin{aligned}
\dot{I}_{msm} &= [p_{msm2msm}I_{msm} + (1 - p_{gpf2gpm})I_{msm}] \lambda(t) - \gamma I_{msm}  \\
\dot{I}_{gpf} &= [p_{gpf2gpm}I_{gpf} + (1 - p_{msm2msm})I_{gpf}] \mu(t) - \gamma I_{gpf}  \\
\dot{I}_{gpm} &= (male_xI_{gpm}) \mu(t) - \gamma I_{gpm}
\end{aligned}







$gpf$, $gpm$, $msm$, and $src$ are the demes of our model, and are represented in R as:
```{r}
demes <- c('gpm', 'gpf', 'msm', 'src')
```



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
