---
title: "Senegal HIV model"
author: "Fabricia F. Nascimento"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Senegal HIV model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette will demonstrate how to estimate HIV transmission rates using DNA sequences from Senegal. This also provides a guidance on how analysis described in Nascimento, (...), Volz, 2018 was carried out.

## The Model
The model we fit is based on the structured coalescent models (ref). These models are used to estimate epidemiological parameters using a phylogenetic tree and information on states of each tip of the tree. Theses states are discrete-trait information representing each sequences. In our mathematical model we have 4 different discrete-traits:

* `gpf` = HIV sample from the general population - females;
* `gpm` = HIV sample from the general population - males;
* `msm` = HIV sample from men that have sex with other men;
* `src` = source sample, which are HIV sample from individuals that are not from other countries and not from Senegal 

These

Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
